\tealeaves: an R package for modelling leaf temperature using energy budgets

### 2019-07-26 ms/ms.Rnw
accepted version

\title{\tealeaves: an R package for modelling leaf temperature using energy budgets}
\author{}
% \author[1]{Christopher. D. Muir}
% \affil[1]{Department of Botany, University of Hawai'i, Honolulu, Hawai'i 96822, USA}
\date{} % delete this line to display the current date

\begin{center}
Tools 
\end{center}

@@

% Phone: +1 808-688-3478 \\
% Email: cdmuir@hawaii.edu \\
% \\
% Funding: University of Hawai'i

@@

>>>>

\title{\tealeaves: an R package for modelling leaf temperature using energy budgets}
\author[1]{Christopher. D. Muir}
\affil[1]{Department of Botany, University of Hawai'i, Honolulu, Hawai'i 96822, USA}
\date{} % delete this line to display the current date

\begin{center}
Form \& Function: Tools 
\end{center}

@@

Phone: +1 808-688-3478 \\
Email: cdmuir@hawaii.edu \\
\\
Funding: University of Hawai'i

@@

\section*{Data:}

Annotated source code to generate this manuscript is available on GitHub (https://github.com/cdmuir/tealeaves-ms) and archived on Zenodo (https://doi.org/10.5281/zenodo.XXXXXX). A development version of \tealeaves~is currently available on GitHub (https://github.com/cdmuir/tealeaves) and the version used for this manuscript is archived on Zenodo (https://doi.org/10.5281/zenodo.2808079).
